A quantum parallel Markov chain Monte Carlo

### 2023-01-20 manuscript/main.tex
letter
begun response to rev 1

%\input{make-edits}
%\makeatletter
%\def\title@font{\Huge}
%\let\ltx@maketitle\@maketitle
%\def\@maketitle{\bgroup%
%	\let\ltx@title\@title%
%	\def\@title{\resizebox{\textwidth}{!}{%
%			\mbox{\title@font\ltx@title}%
%	}}%
%	\ltx@maketitle%
%	\egroup}
%\makeatother

@@

We propose a novel quantum computing strategy for parallel MCMC algorithms that generate multiple proposals at each step. This strategy makes parallel MCMC amenable to quantum parallelization by using the Gumbel-max trick to turn the generalized accept-reject step into a discrete optimization problem.  When combined with new insights from the parallel MCMC literature, such an approach allows us to embed target density evaluations within a well-known extension of Grover's quantum search algorithm.  Letting $P$ denote the number of proposals in a single MCMC iteration, the combined strategy reduces the number of target evaluations required from $\order{P}$ to $\order{P^{1/2}}$.  In the following, we review the rudiments of quantum computing, quantum search and the Gumbel-max trick in order to elucidate their combination for as wide a readership as possible.

@@

\section{Discussion}

@@

>>>>

\input{make-edits}
%\makeatletter
%\def\title@font{\Huge}
%\let\ltx@maketitle\@maketitle
%\def\@maketitle{\bgroup%
%	\let\ltx@title\@title%
%	\def\@title{\resizebox{\textwidth}{!}{%
%			\mbox{\title@font\ltx@title}%
%	}}%
%	\ltx@maketitle%
%	\egroup}
%\makeatother

@@

We propose a novel hybrid quantum computing strategy for parallel MCMC algorithms that generate multiple proposals at each step. This strategy makes the rate-limiting step within parallel MCMC amenable to quantum parallelization by using the Gumbel-max trick to turn the generalized accept-reject step into a discrete optimization problem.  When combined with new insights from the parallel MCMC literature, such an approach allows us to embed target density evaluations within a well-known extension of Grover's quantum search algorithm.  Letting $P$ denote the number of proposals in a single MCMC iteration, the combined strategy reduces the number of target evaluations required from $\order{P}$ to $\order{P^{1/2}}$.  In the following, we review the rudiments of quantum computing, quantum search and the Gumbel-max trick in order to elucidate their combination for as wide a readership as possible.

@@

\section{Discussion}\label{sec:disc}

@@

Nonetheless, there are major technical barriers to the practical implementation of QPMCMC.  The framework, like other hybrid quantum machine learning schemes, requires on-loading and off-loading classical data to and from a quantum machine.  In the seminal review on the subject quantum machine learning, \citet{biamonte2017quantum} discuss the `input problem' in the unnumbered section entitled \textbf{Reading classical data into quantum machines}.  QPMCMC is an overarching framework that is valid for multiple data representations, and different representations suffer from the input problem more than others.     On the one hand, continuous targets require reading $\order{P}$ real vectors onto the quantum machine.  If one follows \citet{jordan2005fast} and opts for a fixed precision representation of each $\ttheta_p\in \mathbb{R}^D$

Conveniently, the `output problem' is less of an issue for QPMCMC, as only a single integer $\hat{p} \in \{0,\dots,P\}$ need be extracted.

### 2023-01-20 manuscript/revision_letter.tex
begun response to rev 1

@@

@@

>>>>

\newcommand{\ttheta}{\boldsymbol{\theta}}
\newcommand{\Ttheta}{\boldsymbol{\Theta}}
\newcommand{\dd}{\mbox{d}}
\newcommand{\ppsi}{\boldsymbol{\psi}}
\newcommand{\U}{\mathbf{U}}
\newcommand{\I}{\mathbf{I}}
\renewcommand{\H}{\mathbf{H}}
\newcommand{\A}{\mathbf{A}}
\newcommand{\B}{\mathbf{B}}
\newcommand{\G}{\mathbf{G}}
\newcommand{\ppi}{\boldsymbol{\pi}}
\newcommand{\llambda}{\boldsymbol{\lambda}}

@@

\begin{reply}
	I thank the Reviewer for taking the time to review the manuscript and for their positive reception.
\end{reply}

@@

\begin{reply}
	I have clarified the hybrid nature of the QPMCMC computing scheme.  The first two sentences of the abstract now read:
	\begin{quote}
		We propose a novel hybrid quantum computing strategy for parallel MCMC algorithms that generate multiple proposals at each step. This strategy makes the rate-limiting step within parallel MCMC amenable to quantum parallelization by using the Gumbel-max trick to turn the generalized accept-reject step into a discrete optimization problem.
	\end{quote}

	In response to the Reviewer's important points regarding on-loading and off-loading data to and from the quantum machine, I have added the step $\ket{\theta_p} \leftarrow \ttheta_p$ within Algorithm \ref{alg:qpMCMC}, along with the comment ``\verb|Load proposal onto quantum computer.|''. Algorithm 4, which is nested within Algorithm 6, already addresses extraction.  Perhaps more importantly, I have added the following paragraph to the Discussion (Section \ref{sec:disc}):

	\begin{quote}
		Quote
	\end{quote}
\end{reply}
